Ms 1

### 2017-09-28 ms1/ms1_display.Rmd
ms1: first fills

@@

# compute risk ratios
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_approp_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p) # now estimate is adjusted change
```

ggplot(adjusted_changes, aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_hline(yintercept=0) +
  geom_bar(dat=adjusted_changes, stat='identity', fill=NA, color='black') +
  geom_errorbar(dat=adjusted_changes, width=0.5) +
  geom_point(dat=unadjusted_changes, aes(ymin=NULL, ymax=NULL), shape=1) +
  geom_point(dat=pde_approp_trends, color='blue', shape=1) +
  geom_errorbar(dat=pde_approp_trends, width=0.25, color='blue') +
  coord_flip() +
  xlab('') +
  ylab('adjusted change from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 32), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_classic() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))

### Adjusted changes in usage

>>>>

### All fills

Bars show adjusted trends in usage, including refills. The dots shows unadjusted trends.

### First fills

Bars show the adjusted change in prescribing, considering only first fills. The blue dots show the change in inappropriate prescribing (which only includes first fills).

@@

# compute risk ratios
pde_approp_trends = read_tsv('tables/pde_approp_trends.tsv') %>%
  filter(term=='year') %>%
  mutate(estimate=exp(3*estimate), # odds ratio over the whole time period
         std.error=sqrt(3)*std.error,
         adj.p=p.adjust(p.value, method='BH'),
         ci=1.96*std.error,
         ci_low=estimate-ci,
         ci_high=estimate+ci) %>%
  left_join(pde_approp_risk_2011, by='antibiotic') %>%
  # convert OR to RR (i.e., adjusted change)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) risk_ratio_f(x, .$risk_2011 - 1)) %>%
  # convert to percents, and reverse direction (to make it *inapprop*)
  mutate_at(vars(estimate, ci_low, ci_high), function(x) -(x - 1)*100) %>%
  select(antibiotic, pct_change=estimate, ci_low, ci_high, adj.p)
  # now estimate is adjusted change in INappropriate prescribing

adjusted_changes_firstfill = read_tsv('tables/model_abx_firstfill.tsv') %>%
  rename(antibiotic=name) %>%
  filter(term=='year') %>%
  mutate(estimate=3*estimate,
         std.error=sqrt(3)*std.error) %>%
  model_ci() %>%
  select(antibiotic, pct_change, ci_low, ci_high) %>%
  arrange(pct_change) %>%
  mutate(antibiotic=fct_inorder(antibiotic),
         antibiotic=fct_relevel(antibiotic, 'overall', after=Inf))

ggplot(adjusted_changes_firstfill, aes(x=antibiotic, y=pct_change, ymin=ci_low, ymax=ci_high)) +
  geom_hline(yintercept=0) +
  geom_bar(stat='identity', fill=NA, color='black') +
  geom_errorbar(width=0.5) +
  geom_point(dat=pde_approp_trends, color='blue', shape=1) +
  geom_errorbar(dat=pde_approp_trends, width=0.25, color='blue') +
  coord_flip() +
  xlab('') +
  ylab('adjusted change from 2011 to 2014 (%)') +
  scale_y_continuous(limits=c(-22, 35), breaks=c(-20, -10, 0, 10, 20, 30)) +
  theme_classic() +
  theme(axis.title.x = element_text(size=16),
        axis.text = element_text(size=16))
```

### Adjusted changes in usage table
